Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-17 Paper/intro.tex
sec 2 ...

\alennote{The structure of the paper is mostly okay; I have one recommendation:
(i) make section 2.1 a separate section called preliminaries on active subspaces (or 
something like that); (ii) make section 2.2. a section of its own, with a more descriptive
section heading. The way things stand, people might take our section 2.2. as just background materials}
This article is organized as follows. In section~\ref{sub:ac}, a brief
theoretical background on the active subspace methodology is provided. In
section~\ref{sub:gsa}, it is shown that the activity scores provide a
reasonable approximation to the DGSMs especially in a high-dimensional setting.
Additionally, a relationship between the three global sensitivity measures,
namely, the activity scores, DGSMs, and the total Sobol' indices is
established. In section~\ref{sec:method}, a systematic framework for computing
the active subspace using an iterative gradient-based approach is provided.
Numerical results based on the gradient-free approach are compared with those
obtained using the gradient-based approach.  The active subspace is computed
for the H$_2$/O$_2$ reaction kinetics problem whereby only the $A_i$'s are
considered as uncertain. In this case, the two approaches are observed to yield
consistent results. In section~\ref{sec:app}, the gradient-based approach is
further implemented to compute the active subspace for the high-dimensional
H$_2$/O$_2$ reaction kinetics problem. The resulting active subspace is found
to be 1-dimensional thereby indicating enormous potential for computational
savings in this application. The active subspace is also computed using the
gradient-free approach. It is observed that although the uncertainty in the
ignition delay is reasonably approximated, the gradient-free approach fails to
capture the global sensitivity of all the uncertain inputs. Hence, a trade-off
between efficiency and accuracy between the two approaches is observed in this
case.  Finally, a summary and discussion based on our findings is included in
section~\ref{sec:conc}.

>>>>

\alennote{Okay, I reorganized the sections a bit (new sec 2, 3); please read the following and
make sure it reflects the contents of the sections correctly.}
This article is organized as follows. In section~\ref{sub:ac}, a brief
theoretical background on the active subspace methodology is provided. In
section~\ref{sub:gsa}, it is shown that the activity scores provide a
reasonable approximation to the DGSMs especially in a high-dimensional setting.
Additionally, a relationship between the three global sensitivity measures,
namely, the activity scores, DGSMs, and the total Sobol' indices is
established. In section~\ref{sec:method}, a systematic framework for computing
the active subspace using an iterative gradient-based approach is provided.
Numerical results based on the gradient-free approach are compared with those
obtained using the gradient-based approach.  The active subspace is computed
for the H$_2$/O$_2$ reaction kinetics problem whereby only the $A_i$'s are
considered as uncertain. In this case, the two approaches are observed to yield
consistent results. In section~\ref{sec:app}, the gradient-based approach is
further implemented to compute the active subspace for the high-dimensional
H$_2$/O$_2$ reaction kinetics problem. The resulting active subspace is found
to be 1-dimensional thereby indicating enormous potential for computational
savings in this application. The active subspace is also computed using the
gradient-free approach. It is observed that although the uncertainty in the
ignition delay is reasonably approximated, the gradient-free approach fails to
capture the global sensitivity of all the uncertain inputs. Hence, a trade-off
between efficiency and accuracy between the two approaches is observed in this
case.  Finally, a summary and discussion based on our findings is included in
section~\ref{sec:conc}.
